TO CHANGE: Web Service Community \\ Learning

### 2014-07-11 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\subsection{The join challenge}\label{s:tjc}

@@

*******THIS ONE IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******
In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
*******THIS ONE IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******

>>>>

\subsection{The Join Challenge}\label{s:tjc}
Sometimes web services can increase their overall utility by starting a collaboration with other web services as communities. This collaboration can help them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters. The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration.

@@

*******SOME PARTS IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******
In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
*******SOME PARTS IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******
